### 2017-05-11 paper/evaluation.tex
minor tweaks
minor changes

Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{wrapfigure}
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
the distribution of answers.

@@

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
abbreviated project names.  Columns ``\emph{Group}'' and
``\emph{Name}'' indicate, respectively, the group and the name of the
subject.  Column ``$T_s$'' shows sequential execution time and column
``$T_p$'' shows parallel execution time. Column ``$T_s/T_p$'' shows
the speedup or slowdown.  As usual, a ratio above 1x denotes speedup
and a ratio below 1x denotes slowdown.

\begin{figure}[h!]
\centering
\resizebox{.45\textwidth}{!}{%
\scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Highest slowdown/speedup appears in gray color.}
\label{tab:speedup}
\end{figure}

>>>>

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{wrapfigure}
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  The pie chart in Figure~\ref{fig:rq5-answers} 
summarizes the distribution of answers.

@@

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
project names.  Columns ``\emph{Group}'' and
``\emph{Name}'' indicate, respectively, the group and the name of the
subject.  Column ``$T_s$'' shows sequential execution time and column
``$T_p$'' shows parallel execution time. Column ``$T_s/T_p$'' shows
speedup or slowdown.  As usual, a ratio above 1x denotes speedup
and a ratio below 1x denotes slowdown.

\begin{figure}[h!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Highest slowdown/speedup appears in gray color.}
\label{tab:speedup}
\end{figure}
